\sysfull

### 2018-04-16 paper/background.tex
section 2 done

Checkpoints of volatile state preserve intermittent progress, but do not ensure data consistency~\cite{dino,chain,ratchet}. Data may become inconsistent if an attempt to execute some computation {\em writes} to a non-volatile variable, then power fails, then a second attempt to re-execute the same computation incorrectly {\em reads} the value written in the first attempt, rather than the variable's original value. The situation occurs when code includes a WAR dependence between operations that manipulate non-volatile variables~\cite{ratchet,dino,alpaca}---see Figure~\ref{fig:code_demo_incosistency} that illustrates how state can become inconsistent in an intermittent execution using the cyclic redundancy check (CRC) code from MIBench2~\cite{hicks_mibench2_2016}.
%Figure~\ref{fig:code_demo_incosistency} illustrates how state can become inconsistent in an intermittent execution using the cyclic redundancy check (CRC) code from MIBench2~\cite{hicks_mibench2_2016}. The code computes the CRC for an $\texttt{nBytes}$ byte message $\texttt{msg}$ with remainder $\texttt{Rmnd}$.
%Despite checkpointing at line 3 in Fig.~\ref{fig:crc_example}, the code may compute  $\texttt{data}$ incorrectly because of the read of $\texttt{Rmnd}$ on line 4 and the write of $\texttt{Rmnd}$ on line 5. Figure~\ref{fig:crc_example_war} shows an intermittent execution. The second iteration writes $\texttt{Rmnd}$, but power fails before the checkpoint. After restarting, line 9 reads the updated value of $\texttt{Rmnd}$, producing an incorrect $\texttt{data}$ value. Checkpoint-based systems risk violating memory consistency~\cite{dino}. 
To maintain consistency, prior systems~\cite{dino,ratchet} {\em version} a subset of non-volatile data with the checkpoint. Task-based systems~\cite{chain,alpaca}, which we focus on, ensure consistency using programmer, compiler, and runtime support.

@@

\textbf{Fixed-size Tasks are Inflexible and Inefficient.} If a programmer writes a task that consumes {\em more} energy than the device can buffer, the task will never complete using buffered energy {\em preventing forward progress} by repeatedly re-executing. If a programmer writes tasks that consume far {\em less} energy than a device can buffer, the system may operate {\em inefficiently}. When a task and its successor both complete, the two tasks were interleaved by a task boundary that preserves progress and state (i.e., checkpoint or commit). However, absent a power failure, the work to preserve state was {\em unnecessary}, incurring overhead on the tasks' executions.

Avoiding excessively costly, non-terminating tasks and short, high-overhead tasks is a programming challenge, given fixed hardware (no support from dedicated circuitry to measure the state of energy buffer) with a fixed energy buffering capacity. Buffer sizes from prior work on intermittently-powered computing hardware vary widely from 20\,$\mu $F~\cite{rodriguez_tbcs_2015} to 0.1\,F~\cite{moo}. Sizing tasks complicates {\em porting} code from one device to another. An excessively costly task on a device with a small energy buffer may be a relatively short task on a device with a larger buffer. The key problem is that using existing systems, by defining tasks statically for a fixed energy buffer, the programmer either risks non-termination or poor performance due to high overhead. \sys's execution model based on {\em task coalescing}---merging or dissecting multiple tasks {\em during} execution based on the program execution behavior, and {\em task downscaling}---shortening task boundaries during execution when even the smallest task does not fit the energy buffer, both models described in Section~\ref{sec:task_adaptation}, is motivated by these observations.

>>>>

Checkpoints of volatile state preserve intermittent progress, but do not ensure data consistency~\cite{dino,chain,ratchet}. Data may become inconsistent if an attempt to execute some computation {\em writes} to a non-volatile variable, then power fails, then a second attempt to re-execute the same computation incorrectly {\em reads} the value written in the first attempt, rather than the variable's original value. The situation occurs when code includes a \emph{write-after-read} (WAR) dependence between operations that manipulate non-volatile variables~\cite{ratchet,dino,alpaca}---see Figure~\ref{fig:code_demo_incosistency} that illustrates how state can become inconsistent in an intermittent execution using the cyclic redundancy check (CRC) code from MIBench2~\cite{hicks_mibench2_2016}.
%Figure~\ref{fig:code_demo_incosistency} illustrates how state can become inconsistent in an intermittent execution using the cyclic redundancy check (CRC) code from MIBench2~\cite{hicks_mibench2_2016}. The code computes the CRC for an $\texttt{nBytes}$ byte message $\texttt{msg}$ with remainder $\texttt{Rmnd}$.
%Despite checkpointing at line 3 in Fig.~\ref{fig:crc_example}, the code may compute  $\texttt{data}$ incorrectly because of the read of $\texttt{Rmnd}$ on line 4 and the write of $\texttt{Rmnd}$ on line 5. Figure~\ref{fig:crc_example_war} shows an intermittent execution. The second iteration writes $\texttt{Rmnd}$, but power fails before the checkpoint. After restarting, line 9 reads the updated value of $\texttt{Rmnd}$, producing an incorrect $\texttt{data}$ value. Checkpoint-based systems risk violating memory consistency~\cite{dino}. 
To maintain consistency, prior systems~\cite{dino,ratchet} {\em version} a subset of non-volatile data with the checkpoint. Task-based systems~\cite{chain,alpaca}, which we focus on, ensure consistency using programmer, compiler, and runtime support.

@@

\textbf{Fixed-size Tasks are Inflexible and Inefficient.} If a programmer writes a task that consumes {\em more} energy than the device can buffer, the task will never complete using buffered energy {\em preventing forward progress} by repeatedly re-executing. If a programmer writes tasks that consume far {\em less} energy than a device can buffer, the system may operate {\em inefficiently}. When a task and its successor both complete, the two tasks were interleaved by a task boundary that preserves progress and state (i.e., checkpoint or commit). However, absent a power failure, the work to preserve state was {\em unnecessary}, incurring overhead on the tasks' executions. Avoiding excessively costly, non-terminating tasks and short, high-overhead tasks is a programming challenge, given fixed hardware (no support from dedicated circuitry to measure the state of energy buffer) with a fixed energy buffering capacity. Buffer sizes from prior work on intermittently-powered computing hardware vary widely from 20\,$\mu $F~\cite{rodriguez_tbcs_2015} to 0.1\,F~\cite{moo}. Sizing tasks complicates {\em porting} code from one device to another. An excessively costly task on a device with a small energy buffer may be a relatively short task on a device with a larger buffer. The key problem is that using existing systems, by defining tasks statically for a fixed energy buffer, the programmer either risks non-termination or poor performance due to high overhead. \sys's execution model based on {\em task coalescing}---merging or dissecting multiple tasks {\em during} execution based on the program execution behavior, and {\em task downscaling}---shortening task boundaries during execution when even the smallest task does not fit the energy buffer, both models described in Section~\ref{sec:task_adaptation}, is motivated by these observations. The main enabler for task coalescing is \emph{memory virtualization} that resolves dynamic WAR dependencies, which is described in Section~\ref{sec:memory_virtulaization}.
